---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pinsqs

**pinsqs** provides convenience functions to incorporate multithreaded reading and writing of `.qs`
files from the [qs](https://github.com/qsbase/qs) package into the
[pins](https://github.com/rstudio/pins-r/) infrastructure.

Motivated by this [feature request](https://github.com/rstudio/pins-r/issues/725) that does have any
plans for implementation in the near future, as I felt its use (and reuse) could benefit my own
workflows.

## Installation

You can install this package using:

``` r
# install.packages("remotes")
remotes::install_github("adamoshen/pinsqs")
```

## Example usage

```{r}
library(tibble)
library(magrittr)
library(pins)
library(pinsqs)
```

Initialise the pin board, as usual:

```{r}
board <- board_temp()
```

Create data to be pinned:

```{r}
rock <- datasets::rock %>%
  as_tibble()
```

Pin the data to the board (as a `.qs` file):

```{r}
board %>%
  pin_qsave(
    rock, "rock-tibble",
    description = "`rock` data set as a tibble"
  )
```

Checking the contents of our pin board, as usual:

```{r}
board %>%
  pin_search()
```

View pin metadata, as usual:

```{r}
board %>%
  pin_meta("rock-tibble")
```

Read the pinned data (from a `.qs` file):

```{r}
board %>%
  pin_qread("rock-tibble")
```

## Notes

If a value for `nthreads` is not supplied to `pin_qread()` or `pin_qsave()`, it will default to
`parallel::detectCores() / 2`. Otherwise, if `parallel::detectCores()` is `NA`, it will fallback to
the default of the [qs](https://github.com/qsbase/qs) package, which is 1.
